### 2014-01-08 msc-thesis/chapters/1/chapter-intro.tex
MSC draft 1 complete.

% There are 4 studies
Clearly, indirect conflicts and its subsequent research areas have a large breadth of limitations, some of which
will be explored in this dissertation. In order to fully understand indirect conflicts, this dissertation is composed
of 4 studies of which explore different components of indirect conflicts.

@@

In order to fully understand the root causes of information overload, false positives, and
scalability issues in regards to indirect conflicts, Study 3 was an empirical study to determine what events occur to
cause indirect conflicts, when they occur, and if conditions exist to provoke more of these events. 
I also set out to understand what mitigation strategies developers currently use as opposed to those created
by academia. Through this exploration, I looked to find what can be accomplished moving forward with indirect conflicts
in both research and industry. I interviewed 19 developers from across 12 commercial and open source projects, followed by a confirmatory survey of 78 
developers, and 5 confirmatory interviews, in order to answer the aforementioned questions. My findings indicate that: 
indirect conflicts occur frequently and are likely caused by software contract changes and a lack of understanding of those changes,
developers tend to prefer to use detection and resolution processes or tools
over those of prevention, developers do not want awareness mechanisms which provide non actionable results, 
and there exists a gap in software evolution analytical tools from the reliance on static analysis resulting in missed
context of indirect conflicts. As a result of the final finding (the gap in software evolution analytical tools), I conducted
a fourth and final study.

>>>>

% What is being addressed in this thesis
Clearly, indirect conflicts and its subsequent research areas have a large breadth of limitations, some of which
will be explored in this dissertation. I will look to explore: technical dependencies, how developers are involved,
socio-technical congruence as a mitigation strategy to indirect conflicts, what the root causes of indirect conflicts are,
what compounding factors exist for indirect conflicts, what current industry mitigation strategies of indirect conflicts
are being used, what future steps should be taken in academia to better industry regarding indirect conflicts, and finally,
how software evolution analysis can be used to better tools for indirect conflicts. I will address these issues by
conducting the following four studies.

@@

In order to fully understand the root causes of information overload, false positives, and
scalability issues in regards to indirect conflicts, Study 3 was an empirical study to determine what events occur to
cause indirect conflicts, when they occur, and if conditions exist to provoke more of these events. 
I also set out to understand what mitigation strategies developers currently use as opposed to those created
by academia. Through this exploration, I looked to find what can be accomplished moving forward with indirect conflicts
in both research and industry. This study asked the following 3 research questions: 
\textit{What events or conditions lead to indirect conflicts?}
\textit{What mitigation techniques are used by developers in regards to indirect conflicts?}
\textit{What do developers want from future indirect conflict tools?}

 I interviewed 19 developers from across 12 commercial and open source projects, followed by a confirmatory survey of 78 
developers, and 5 confirmatory interviews, in order to answer the aforementioned questions. My findings indicate that: 
indirect conflicts occur frequently and are likely caused by software contract changes and a lack of understanding of those changes,
developers tend to prefer to use detection and resolution processes or tools
over those of prevention, developers do not want awareness mechanisms which provide non actionable results, 
and there exists a gap in software evolution analytical tools from the reliance on static analysis resulting in missed
context of indirect conflicts. As a result of the final finding (the gap in software evolution analytical tools), I conducted
a fourth and final study.

### 2014-01-08 msc-thesis/chapters/3/sec-iced.tex
MSC draft 1 complete.

In order to fully understand the root causes of information overload, false positives, and
scalability issues in regards to indirect conflicts, I conducted an empirical study to determine what events occur to
cause indirect conflicts, when they occur, and if conditions exist to provoke more of these events. 
I then set out to understand what mitigation strategies developers currently use as opposed to those created
by academia. Through this exploration, I look to find what can be accomplished moving forward with indirect conflicts
in both research and industry.

>>>>

In order to fully understand the root causes of information overload, false positives, and
scalability issues in regards to indirect conflicts, I conducted an empirical study to determine what events occur to
cause indirect conflicts, when they occur, and if conditions exist to provoke more of these events. 
I then set out to understand what mitigation strategies developers currently use as opposed to those created
by academia. Through this exploration, I look to find what can be accomplished moving forward with indirect conflicts
in both research and industry. My research questions for this particular study are as follows:

\begin{description}
        \item[RQ1\namedlabel{itm:rq1}{RQ1}] \textit{What events or conditions lead to indirect conflicts?}
        \item[RQ2\namedlabel{itm:rq2}{RQ2}] \textit{What mitigation techniques are used by developers in regards to indirect conflicts?}
        \item[RQ3\namedlabel{itm:rq3}{RQ3}] \textit{What do developers want from future indirect conflict tools?}
\end{description}
